### 2020-02-04 ncov.tex
more tweaks

In this study, we focused on propagating errors arising from implicit or explicit estimates of growth rate and generation intervals.
These estimates of the exponential growth rate depend on how incidence has been reported.
For emerging pathogens such as 2019-nCoV, we expect the reporting rate to increase over time due to limited resources and uncertainty in case definition initially;
for example, \cite{zhaoncov} (Study 6) found that that estimates of \Ro could change from 5.47 (95\% CI: 4.16--7.10) to 3.30 (95\% CI: 2.73--3.96) when they assume 2-fold changes in the reporting rate between January 16--20.

Other key issues underlying early estimates of \Ro include statistical independence and types of noise.

@@

There are other important phenomena not covered by our simple framework. Examples that seem relevant to this outbreak include: changing reporting rates, changing generation intervals, and reporting delays (including the effects of weekends and holidays.)
\jd{This \P\ should be fleshed out and citated.}

@@

We reviewed 6 modeling studies of the novel coronavirus outbreak that were published online between January 23 and January 26, 2020 (Table 1).
Five studies \citep{liuncov, majumderncov, readncov, riouncov, zhaoncov} were uploaded to pre-print servers (bioRxiv, medRxiv, and SSRN), and one report was posted on the website of Imperial College London \citep{imaincov}.
They vary widely in their statistical methods and in the amount of data used to infer \Ro.
\cite{imaincov} and \cite{riouncov} simulated branching process models and compared the predicted number of cases from their models with the estimated number of total cases by January 18.
\cite{readncov} fitted a deterministic, metapopulation Susceptible-Exposed-Infected-Recovered (SEIR) model to incidence data between January 1 and January 21 from major cities in China and other countries.
\cite{zhaoncov} and \cite{liuncov} fitted exponential growth models to incidence data up to January 22 and January 23, respectively, and inferred \Ro via the Euler-Lotka equation (\eref{euler}).
\cite{majumderncov} fitted the Incidence Decay and Exponential Adjustment (IDEA) model \citep{fisman2013idea} to incidence data up to January 26, which is equivalent to fitting an exponential growth model and assuming a fixed generation-interval distribution.

>>>>

In this study, we focused on propagating errors arising from implicit or explicit estimates of growth rate and generation intervals.
Other key issues underlying early estimates of \Ro include statistical independence and types of noise.

@@

There are other important phenomena not covered by our simple framework. 
Examples that seem relevant to this outbreak include: changing reporting rates, reporting delays (including the effects of weekends and holidays), and changing generation intervals.
For emerging pathogens such as 2019-nCoV, we expect the reporting rate to increase over time due to limited resources and uncertainty in case definition initially;
for example, \cite{zhaoncov} (Study 6) found that that estimates of \Ro could change from 5.47 (95\% CI: 4.16--7.10) to 3.30 (95\% CI: 2.73--3.96) when they assume 2-fold changes in the reporting rate between January 16--20.

\jd{This \P\ should be fleshed out and citated.}

@@

We reviewed 7 modeling studies of the novel coronavirus outbreak that were published online between January 23 and January 26, 2020 (Table 1).
Five studies \citep{liuncov, majumderncov, readncov, riouncov, zhaoncov} were uploaded to pre-print servers (bioRxiv, medRxiv, and SSRN); one report was posted on the website of Imperial College London \citep{imaincov}; and one report was posted on nextstrain.org \citep{bedfordncov}.
They vary widely in their statistical methods and in the amount of data used to infer \Ro.
\cite{bedfordncov}, \cite{imaincov}, and \cite{riouncov} simulated branching process models and compared the predicted number of cases from their models with the estimated number of total cases by January 18 (between 1,000 and 9,7000 \citep{imaincov0}).
\cite{readncov} fitted a deterministic, metapopulation Susceptible-Exposed-Infected-Recovered (SEIR) model to incidence data between January 1 and January 21 from major cities in China and other countries.
\cite{zhaoncov} and \cite{liuncov} fitted exponential growth models to incidence data up to January 22 and January 23, respectively, and inferred \Ro via the Euler-Lotka equation (\eref{euler}).
\cite{majumderncov} fitted the Incidence Decay and Exponential Adjustment (IDEA) model \citep{fisman2013idea} to incidence data up to January 26, which is equivalent to fitting an exponential growth model and assuming a fixed generation-interval distribution.
